---
title: "Homework08"
output: html_document
---

# HW08: Using and building packages in R.

##Getting my home computer ready for package production
One of the perils of havign two computers to work on (after conflicting directory palths as I discovered last class) is that I need to get softwere thigns up twice.  That's ok, more practise right?

So first off I need to [configure for package devel](https://stat545-ubc.github.io/packages01_system-prep.html)

###1. I check version
Am I using the latest version of RStudio, Version 0.99.486 no new updates.  So I think that step is done.

###2. I install `devtools`
```{r}
install.packages("devtools")
library(devtools)
```

###3. I download and install RTools.  
After waiting for a bit for things to install I restart and check that everything is going smoothly.

```{r}
library(devtools)
find_rtools()

has_devel()
```

###4. Other packages 

This needs some other packages apparently so I'll make sure I've got those.
```{r}
install.packages("roxygen2")
install.packages("testthat")
install.packages("knitr")
```

## Package Initiation
Now I want to create the folder that will hold the package.

```{r}
library(devtools)
create("~/foofactors")
```

Hmm, that isn't where I thought it would go.  I thought the `~` would put it in as subdirectory of my current wd.  But instead it went to my general `Documents` folder.  Booo.

```{r}
wd <- getwd()
create(sprintf("%s/foofactors",wd))
```

That seems to have done the ticket!  Much better.
But I think the .Rproj file is redundant since I've already got one. I'll deleat it and hope someone will help me when that results in calamity.
